---
title: 'Data Products: Week 4 assignement'
author: "Eric"
date: "October 27, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, comment = FALSE, message=FALSE)
library(cluster)
```

## Iris dataset summary
The application is a simple example on kmean clustering applied on the Iris dataset  


```{r iris}
summary(iris)
```

The example application uses the kmeans() function in R   
  
the number of centers can get select with the slider (from 2 to 4)  
The example in this presentation uses 3 centers  



```{r kmeans, echo=FALSE}

myiris <- iris
myiris$Species <- NULL
km <- kmeans(myiris, 3)
```

## Iris clustering

the table displays the coordinates of the centers   

```{r kmcenters}
km$centers
```

  
There are a number of plots displayed in two groups  
   that may get hidden / shown using the tickboxes   
  
## Iris Plot type 1


The first group of two plots contains scatter plots with the Iris data and the found centers  
  

```{r plot 1}
    plot(myiris[c("Sepal.Length", "Sepal.Width")], col=km$cluster)
    points(km$centers[,c("Sepal.Length", "Sepal.Width")], col=1:nrow(km$centers), pch=15, cex=2)
    plot(myiris[c("Petal.Length", "Petal.Width")], col=km$cluster)
    points(km$centers[,c("Petal.Length", "Petal.Width")], col=1:nrow(km$centers), pch=15, cex=2)

```

## Iris Plot type 2

The second group of two plots contains more elaborated graphs  
  - a scatter plot with PCA (clusplot) 
  - a pairwise scatterplot 
  
```{r plot 2}
    clusplot(myiris, km$cluster, color=TRUE, shade=TRUE, 
           labels=2, lines=0)
    with(myiris, pairs(myiris, col=c(1:3)[km$cluster])) 

 
```
